Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-01 thesis/acm/paper.tex
Added some comments to the conclusion

\subsubsection{3\textsuperscript{rd} Party}y e
ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

%%John add conclusion ideas here

>>>>

\subsubsection{3\textsuperscript{rd} Party}
ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)

@@

%%John add conclusion ideas here
We were correct with the majority of our categorisations. The ones we did get wrong were because we did not think of it from specific points of view. This probably means that it's possible to reverse engineer to some extent, but not completely (Which is probably the answer most people would expect).

Interesting that the majority of the changes seem to be driven either by management (Suggested that it comes from partners) or the partners directly. There was also internal pressure to improve the API which came about from Axis developers trying to create their own applications.

Potential ordering:

RQ1
RQ1.1
RQ2
What this means for industry:
	Greater emphasis should be placed upon communicating with the end users / application developers
What this means for academia
